\chapter{Sets and Relations}
\section{Sets}
A set is $\underline{not}$ originally ordered, so:
\[ \{a , b\} = \{b, a\} \]
But sets $\underline{can}$ be ordered under various schemes described below.
\section{Classes and Collections}
\begin{defn}[Class]
	A set consisting of elements that are themselves sets. Sometimes said to be a collection of sets.
\end{defn}
\begin{defn}[Collections]
	A set consisting of sets. Often used in topology instead of the word class.
\end{defn}

\section{Ordered Pairs}
\begin{defn}[Ordered Pair]
	Encodes the order of elements in a set $x, y \in A$:
	\[ (x, y) = \{ \{ x \}, \; \{ x, y \} \} \]
	Sometimes denoted:
	\[ \langle x, y \rangle = \{ \{ x \}, \; \{x, y\} \} \]
\end{defn}
The above comes from Kazimierz Kuratowski in 1921. Amazing how recent things are.

\section{Relations}
\begin{defn}[Relation]
	A set whose elements are ordered pairs. \\
	
	e.g. $A \times B = \{ (x, y) \mid x \in A \; \; y \in B \}$
\end{defn}

\subsection{Ordering Relation}
\begin{defn}[Less Than Relation]
	\[ < (x, y)  = \{ (x, y) \mid \text{x is less than y} \} \]
\end{defn}
This is universally shortened to $x < y$ given it is a binary operator and used so much.
\subsection{Cartesian Products}
\begin{defn}[Cartesian Product $A \times B$]
	The collection/class of all ordered pairs between two sets:
	\[ A \times B = \{ (x, y) \mid x \in A \; \; \; y \in B \} \]
\end{defn}
\subsection{N-ary Ordered Pairs}
\begin{defn}[N Ordered Pairs]
	A relation that encodes the order of the n elements, n=4 shown:
	\[ (x, y, w, z) = (((x, y), w), z)  \]
\end{defn}
\subsection{Function}
\begin{defn}[Function]
	A relation that has one-to-one correspondence between elements of the domain and the range.
\end{defn}
\subsection{Equivalence Relation}
A relation denoted:
\[ a \sim b \]
that satisfies three properties of being:
\begin{enumerate}
	\item Reflexive
	\item Symmetric
	\item Transitive
\end{enumerate}